---
title: "Increase in Covid-19 cases in the US during July 2020"
author: your_name_here
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_document
---

```{r setup, include=FALSE}

library(tidyverse)
library(choroplethrMaps)
library(cowplot)
library(lubridate)
library(knitr)
library(kableExtra)

```

```{r data}

# Read in data sets from last week. No output from this chunk should appear in your document.

```

Which states had the lowest percent increase? Which states had the most?
```{r data-manipulation}

# Manipulate the data, like we did last week, to calculate percent increase across the states.

# Create a table using kable() of each state and percent increase; present states in descending order.

# The document should display the table but not the code.
 
```

Was there a statistically significant increase in cases between the months of June and July in CT?
``````{r t-test}

# Manipulate the data to:
# 1. Only contain CT.
# 2. Only contain observations from June and July.
# 3. Show the number of new cases on each day.

# Conduct a t-test to test whether June and July had, on average, had the same or different number of new cases on any given day of the month

# Display the results, but not the code.
# Challenge exercise: display ONLY the t-statistic.

``` 

```{r map}

# Using the code from last week, draw the map of all 50 states. Display the map but not the code.
# You may notice that Alaska looks weird; try adjusting the height.

```
